Initial Analysis

### 2020-08-03 Scripts/Initial_Analysis.Rmd
Double chekcce all statistics

@@

  }else{
    ggsave(
      plot = Map,
      width = 17,
      height = 12,
      units = "in",
      filename = Plot_Name
    )
  }

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_id,eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area,
            by = c("eez_id","eez_name")
            ) %>%
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

# Douuble check we are not missing EEZs
# Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")

@@

# Variable to plot (value,  catch, weighted_catch, weighted_value)
Variable_plot <- "value"
CreateFigureOne(Variable_plot)

@@

#  Post-hoc analysis
TukeyHSD(Rev_aov) %>% 
  tidy() %>% 
  filter(adj.p.value < 0.05)

@@

### Data for Weighted plot
```{r Weight_Revenue, eval =F, echo =F}
r
Continent_Trans_Value <- Subregion_Trans_raw_Value %>% 
  left_join(Regional_Area,
            by = "sub_region") %>% 
  mutate(
    Value_sum= Value_sum*1000000,
    weighted_value = Value_sum/Size_Region
    )

@@

```{r Sub-regional_differences, eval = F}

# Revenue ANOVA
Subregion_Rev_stats <- Subregion_Data_stats %>%
  filter(Variable == "value")

Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
Rev_aov
summary(Rev_aov)

# Df    Sum Sq Mean Sq F value  Pr(>F)    
# sub_region   16  75628526 4726783    4.91 4.2e-08 ***
# Residuals   157 151140183  962676

#  Post-hoc analysis
TukeyHSD(Rev_aov)

# Northern America sig than everyone except for Eastern Asia
# Eastern Asia sig with everyone except with Eastern Europe and North Am.

>>>>

  ### Labels

@@

  }else{
    plot_all <- ggdraw() +
      # map
      draw_plot(Map, x = 0, y = 0, width = 1, height = 1) #+
      # Revenue circular
      # draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
      # # Catch circular
      # draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
      # # Labeks
      # draw_plot_label(label = c("A", "B"), 
      #                 size = 20,
      #                 x = c(0, 0), 
      #                 y = c(1, 0.45)
      # ) +
      # draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
      #                 size = 8,
      #                 x = c(0.330,0.485), 
      #                 y = c(0.31,0.29)
      # )

    save_plot(
      # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
      Plot_Name,
      plot_all,
      base_height = 5,
      base_width = 8
    )
  }

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    # Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

# Douuble check we are not missing EEZs
Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")

@@

# Variable to plot (value, catch, weighted_catch, weighted_value)
Variable_plot <- "catch"
CreateFigureOne(Variable_plot)

@@

#  Post-hoc analysis
TukeyHSD(Rev_aov) %>% 
  tidy() %>% 
  filter(adj.p.value < 0.05) %>% 
  View()

@@

### Data for Weighted plot
```{r Weight_Revenue, eval =F, echo =F}

Continent_Trans_Value <- Subregion_Trans_raw_Value %>% 
  left_join(Regional_Area,
            by = "sub_region") %>% 
  mutate(
    Value_sum= Value_sum*1000000,
    weighted_value = Value_sum/Size_Region
    )

@@
